---
title: "p8105_hw5_cz2544"
author: "Chunxiao Zhai"
date: "11/3/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)

set.seed(1)
```


## Problem 1
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help

Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r load_zip_data}
file_name = list.files("./data")
vec_file_name = str_c("./data/", file_name)
data = data_frame(file_name, map(vec_file_name, read.csv)) %>%
  unnest %>% 
  mutate(file_name_1 = str_replace(file_name, ".csv", "")) %>% 
  separate(file_name_1, into = c("arm", "id"), sep = "_") %>% 
  gather(key = "week", value = "value", week_1:week_8) %>% 
  mutate(week = as.numeric(str_replace(week, "week_", "")))
```

```{r spaghetti_plot}
data %>% group_by(file_name) %>%  
  ggplot(aes(x = week, y = value, group = file_name, color = arm)) + 
  geom_line()
```
comment: The observation value of experiment group increased along with the time gradually, but the observation value of control group remained the same.

## Problem 2




Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r load_homicide_data}
murder = read.csv("homicide-data.csv")
```
Describe the raw data:
This dataset contains `r nrow(murder)` rows and `r ncol(murder)` columns, with each row resprenting a victim of  homicides over the past decade in 50 of the largest American cities. Variables include case id, reported date, basic demographic information about each victim (name, race, age, sex), geographic information(city, state, longitude and latitude) and despositoin. In total, the cases are from `r n_distinct(murder$city)` cities of `r n_distinct(murder$state)` states, classified into `r n_distinct(murder$disposition)` disposition status.

Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
```{r summarize_city}
city = murder %>% 
  mutate(city_state = str_c("city", "state", sep = ",")) %>% 
  group_by(city, disposition) %>% 
  summarise(n = n()) %>% 
  spread(disposition, n) %>% 
  mutate(n_unsolve = `Closed without arrest` + `Open/No arrest`, n_total = `Closed by arrest`+`Closed without arrest`+ `Open/No arrest`)
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.
```{r prop.test_Baltimore}
Baltimore = city %>% filter(city == "Baltimore") 
prop = prop.test(Baltimore$n_unsolve, Baltimore$n_total) %>% broom::tidy() %>% 
  nest(estimate, conf.low, conf.high) %>% pull(data)
```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and  unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.
```{r prop.test_dataset}
prop_vec = function(data) {
  prop.test(data$n_unsolve, data$n_total)
}

city_nest = city %>% filter(city == "Baltimore") 
  nest(n_unsolve:n_total) %>% 
 
is.list(city_nest$data)
map(city_nest$data, prop_vec)


